%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Example thesis LaTeX document using the fsthesis class
%%
%% Compile with pdflatex
%% However there is option that requires LuaLaTex in the class definition file
%%

\documentclass{fsthesis}

\usepackage{lettrine}   % \lettrine{F}{irst}
\usepackage{titlesec}
\usepackage{natbib}
\usepackage{listings}
\usepackage[acronym,toc,nomain]{glossaries}

% Installed
% texlive-luatex
% texlive-latex-recommended
%   fontspec
% texlive-latex-extra
%   lettrine

% Create the acronyms using a seperate file of definitions
\makeglossaries
\include{acronym_def}

\includeonly{thesis_example_chapter}

\begin{document}
\frontmatter
% Create the titlepage
\title{This is my Thesis\\ \& it's very good...}
\author{Fred Fred}				% author
%\degree{Diploma}				% defaults to 'PhD'
%\university{University of Life}% defaults to 'University of York'
%\dept{School of Hard Knocks}	% defaults to 'Department of Chemistry'
\date{\today}%May 2018}         % standard LaTeX \date behaviour
\maketitle

\tableofcontents
%\pagebreak

\mainmatter


\chapter[Testing chapter]{This is a test chapter and so has areally long title}

\typeout{****}
\typeout{chaptername is \chaptername}
\typeout{textwidth is \the\textwidth}
\typeout{chapboxlength is \the\chapboxlength}
\typeout{chaptitlelength is \the\chaptitlelength}
\typeout{****}

\lettrine{Q}{uam} at parturient a diam ultricies nec phasellus augue scelerisque nec tortor a fringilla a a ullamcorper est ultrices mattis a. Consectetur ac ligula at in adipiscing ad sagittis diam quis scelerisque a mauris etiam dignissim mus enim leo. Per congue \textbf{semper nisl nisl mi scelerisque} porta parturient dignissim ad consectetur \textit{scelerisque cubilia vulputate ante} parturient et eu leo. \textsf{Dis mi euismod lacus pulvinar} curae tortor condimentum mattis enim. \textsc{Condimentum fringilla vestibulum aliquam} elit lobortis mi a ut egestas augue a nunc mollis ultrices. Nec at mollis nostra ullamcorper nam leo commodo cursus adipiscing adipiscing blandit per ut a curae vel eleifend adipiscing vitae justo convallis. This here is a really long URL~\citep{url-01}; \url{https://www.long-long-long-long-long-long.com/long-long-long-long-long-long.html}.

\section{Introduction}
Sit vitae montes dictumst quam \acrfull{WACL} ipsum neque consectetur non litora nisl amet et venenatis egestas ad. Scelerisque tellus adipiscing ornare tempus scelerisque et nam faucibus consectetur adipiscing scelerisque adipiscing a aenean condimentum. Vestibulum \acrshort{WACL} vestibulum \acrfull{FAAM} integer fermentum nam tristique a proin accumsan posuere parturient iaculis parturient aliquam lacinia a sagittis curae condimentum convallis. Adipiscing sodales a egestas aliquam metus ad sociosqu amet venenatis ut ante parturient id mus a iaculis sociis metus parturient imperdiet id.
\par
{\fontsize{20}{25}\selectfont Auctor a ut ut inceptos parturient} torquent metus condimentum a non risus \acrlong{WACL} eu rhoncus consectetur phasellus ultricies arcu sit nunc condimentum nunc amet tristique erat eu ridiculus. Phasellus elementum massa ridiculus \acrfull{bob} ultrices congue nascetur rhoncus eros a sagittis varius aenean cras egestas eu a augue laoreet cum cras phasellus eget hac nostra. \acrshort{bob} in vestibulum porta sapien scelerisque a suspendisse penatibus augue sodales donec egestas adipiscing vitae platea semper urna parturient cubilia phasellus donec id mauris a lorem a pretium parturient dictumst.

\include{thesis_example_chapter}


\appendix
\chapter{A reaction and an equation}
Following are a chemical reaction and then a mathematical equation. Such complicated matters are best described by~\citet{article-01}.
\begin{reaction}
\label{re:A}
A +B \rightarrow C
\end{reaction}
\begin{equation}
\label{eq:A}
A +B = C
\end{equation}

\chapter{Some quicklooks}
\section{Quicklooks for me}
Here are some quicklooks just for me...\citep{book-01}
\begin{reaction}
\label{re:B}
AB+B \rightarrow D
\end{reaction}
% \begin{reaction*}
% \label{re:B}
% O+E \rightarrow 2E
% \end{reaction*}

\section{Quicklooks for you}
These quicklooks are for you (but I sneaked a quick look!). Here I am referencing reactions~\ref{re:A} and \ref{re:B} along with equation~\ref{eq:A}.


\printglossary[type=\acronymtype]

\bibliography{journal-abbrevname,thesis_refs}
\addcontentsline{toc}{chapter}{References}
\bibliographystyle{abbrvnat}

\end{document}